SI: Settlements / Pottery groups

### 2022-04-27 analysis/groups/groups.Rmd
add separate reports for various time resolutions

```{r nested-pca}
# traditions
pca_per <- res_wide %>%
  add_region() %>% 
  group_by(reg, period) %>% 
  nest() %>% 
  nested_pca()
```

@@

>>>>

```{r nested-pca}
pca_per <- res_wide %>%
  add_region() %>% 
  group_by(reg, period) %>% 
  nest() %>% 
  nested_pca()
```

@@

```{r pca-summations}
loadings_sum <- pca_per %>% 
  summarise_variables()
```

```{r pca-summations-hm, eval=FALSE, echo=FALSE}
# loadings_sum_m <- as.matrix(loadings_sum[, paste0("PC", 1:(ncol(loadings_sum) - 1))])
# rownames(loadings_sum_m) <- loadings_sum$column
# heatmap(loadings_sum_m)
```
```{r pca-summations-tb}
loadings_sum %>% 
  mutate(r = (PC1 + PC2 + PC3 + PC4 + PC5)/(ncol(loadings_sum) - 1)) %>% 
  select(column, r) %>% 
  arrange(reg, desc(r)) %>% 
  knitr::kable()
```
